Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-08-10 paper.tex
add note about future code changes

In addition, \texttt{loo.py} allows the user to more easily make changes to the structure of the generated program, e.g., the data ordering, vectorization, and threading patterns, as well as switch the target language for code generation (and more simply extend to additional languages, e.g., CUDA).
Further, \texttt{loo.py} can execute developed subroutines from Python (natively for C code, or via \texttt{PyOpenCL}~\cite{kloeckner_pycuda_2012} for OpenCL), enabling unit testing\slash verification for each component of the Jacobian or source terms; \add{the unit testing suite also helps ensure that bugs are not present in less commonly used code-paths}.
The source terms and sub-components thereof (e.g., rates of progress, pressure-modification terms) are directly compared with Cantera~\cite{Cantera}, while the automatic differentiation code Adept~\cite{hogan2014fast,adept-v11} provides reference values for Jacobian sub-components.
We use the Portable OpenCL (POCL) implementation~\cite{poclIJPP} and OpenMP~\cite{dagum1998openmp} to perform OpenCL and C unit testing, respectively, on the continuous-integration framework Travis CI~\cite{travis:2018}.
We will discuss verification of the complete (as opposed to the sub-component testing discussed here) generated source-terms and Jacobian codes in detail in~\cref{s:verification}.

>>>>

In addition, \texttt{loo.py} allows the user to more easily make changes to the structure of the generated program, e.g., the data ordering, vectorization, and threading patterns, as well as switch the target language for code generation (and more simply extend to additional languages, e.g., CUDA).
Further, \texttt{loo.py} can execute developed subroutines from Python (natively for C code, or via \texttt{PyOpenCL}~\cite{kloeckner_pycuda_2012} for OpenCL), enabling unit testing\slash verification for each component of the Jacobian or source terms; \add{the unit testing suite also helps ensure that bugs are not present in less commonly used code-paths, or introduced by future code changes}.
The source terms and sub-components thereof (e.g., rates of progress, pressure-modification terms) are directly compared with Cantera~\cite{Cantera}, while the automatic differentiation code Adept~\cite{hogan2014fast,adept-v11} provides reference values for Jacobian sub-components.
We use the Portable OpenCL (POCL) implementation~\cite{poclIJPP} and OpenMP~\cite{dagum1998openmp} to perform OpenCL and C unit testing, respectively, on the continuous-integration framework Travis CI~\cite{travis:2018}.
We will discuss verification of the complete (as opposed to the sub-component testing discussed here) generated source-terms and Jacobian codes in detail in~\cref{s:verification}.
